Preliminary results

### 2019-04-01 reports/preliminary_results.Rmd
Some code cleaning and rearrangements of scripts.

I have used data from the "new linkage data base". Primary prosthesis inserted 2008-2015 were included. Note that we should have no problem with censoring here since death dates are recorded up until February 2018. Hence even if patients were operated during 2015, they are not automatically censored at the end of that year. (Censoring would only occour in the case of emigration etc.)
Comorbidity indices based on Elixhauser van Walraven (ECI), Charlson's original index (CCI) and a modified Risk Rx IV index (modified by Anne Garland) were used.

@@

1. Only primaries (no re-operations).
2. Only OA.
3. No hemi.
4. No second bilaterals.
5. No first bilateral if second bilateral inserted within a year.
6. No surface prosthesis
7. Only age 18-100 years
8. only BMI $\leq 50$
9. Only ASA $\leq 3$
10. Exclude if missing education level
11. Exclude if missing marital status level
12. Exclude if missing type of hospital
13. Exclude if fixation data missing

@@

@@

Most of our variables are categorical (very few numeric)

@@

I include all values of each comorbidity index for the moment but those should obviously be truncated/transformed later.

Proportions for most variables are roughly the same as in earlier versions, although not exact due to the extended time frame of the study period.

@@

We have a lot of potential predictors but very few events to predict. This is problematic and we risk overfittnig the model to the data. Hence, if we develop/train our model using all data and then use the same data to evaluate predictive power, the result will look better than it actually is (applying the model to new data will not work as well).

@@

@@

1. General variables
2. Individual ECI diagnosis
3. Individual CCI diagnosis
4. Individual Risk Rx IV diagnosis

@@

```{r}
load("../cache/modsums.RData")
round(modsums$modsum[[1]]$coefmat.full, 2)
```

@@

```{r}
load("../cache/ECI_extremes.RData")
ECI_extremes %>% 
  filter(!ECI_index_walraven %in% -7:21)
```

@@

>>>>

I have used data from the "new linkage data base". Primary prosthesis inserted 2008-2015 were included. Note that we should have no problem with censoring here since death dates are recorded up until February 2018. Hence even if patients were operated during 2015, they are not automatically censored at the end of that year. (Censoring would only occour in the case of emigration etc.)
Comorbidity indices based on the sum of comorbidities recognized by Elixhauser et al. (ECI), Charlson's original index (CCI) and a modified Risk Rx IV index (modified by Anne Garland) were used. Each of those indices were truncated since higher values are rare.

@@

1. Only primaries (no re-operations).
2. Only OA.
3. No hemi.
4. No second bilaterals.
5. No first bilateral if second bilateral inserted within 90 days.
6. No surface prosthesis
7. Only age 18-100 years
8. only BMI $\leq 50$
9. Only ASA $\leq 5$
10. Exclude if missing education level
11. Exclude if missing marital status level
12. Exclude if missing type of hospital
13. Exclude if fixation data missing

@@

We have also used some individual comorbidities recognized by ECI, CCI and Rx and combined those to identify individual comorbidities using an arbitrary source. Those variables are included with suffixes "c_" to their variable names.

@@

Most of our variables are categorical/binary.

@@

Note that some EPVs are low, thus that we have very few observed detahs among some levels! This can make modelleing hard. There is no perfect limit of cases, but 10-20 is commonly recommended and  [@Courvoisier2011] suggested to have at least 5!

@@

We have a lot of potential predictors but very few events to predict (low EPV). This is problematic and we risk overfittnig the model to the data. Hence, if we develop/train our model using all data and then use the same data to evaluate predictive power, the result will look better than it actually is (applying the model to new data will not work as well).

@@

To have such a small estimation set implies however that the observed outcome will be very rare, and the result of validating the model on that data set will be unstable. In this case, the split-sample approach might in fact lead to more confusion. It has been argued by [@Austin2017a] that Bootsrtap-validation is superiod in this case. Another prominent predictive modelling guru, Max Kuhn however, does argue for the need of a separate validation test. The approach used for this project should be further discussed!

@@

1. General variables (including our newly combined comorbidities)
2. Individual ECI diagnosis
3. Individual CCI diagnosis
4. Individual Risk Rx IV diagnosis

@@

```{r}
load("../cache/modsums.RData")
round(modsums$modsum[[1]]$coefmat.full, 2) %>% 
  as_tibble(rownames = "coef") %>% 
  mutate(Est_exp = round(exp(Estimate), 2))
```

@@

```{r}
load("../cache/ECI_extremes.RData")
ECI_extremes %>% 
  filter(!ECI_index_sum_all %in% -7:21)
```

@@

This visualisation was just made up but a similar approach has been suggested by @Greenhill2011.
